Full-core analysis of thorium-fueled molten salt breeder reactor using the SERPENT 2 Monte Carlo code

### 2017-06-24 introduction.tex
resized figures

\begin{figure}[htbp!]
        \begin{center}
                \includegraphics[scale=0.7]{./images/french-transition/power_plot.png}
        \end{center}
        \caption{Timeseries of installed capacity of \gls{SFR}s}
        \label{fig:sfr_cap}
\end{figure}
\FloatBarrier

\begin{figure}[htbp!]
        \begin{center}
                \includegraphics[scale=0.7]{./images/french-transition/number_plot.png}
        \end{center}
        \caption{Timeseries of number of \gls{SFR}s}
        \label{fig:sfr_num}
\end{figure}
\FloatBarrier

@@

\subsection{Reprocessed Uranium}
Reprocessed uranium contains a range of uranium isotopes, from $^{232}U$ to $^{238}U$.
This brings complications in reusing reprocessed uranium as a fuel source \cite{IAEA_management_2007}.
The presence of neutron-absorbing isotopes $^{234}U$ and $^{236}U$ requires reprocessed uranium
to require a higher enrichment of $^{235}U$. There is trace amounts (2 ppb) of fissile istope $^{233}U$,
which provides little benefit.  
Also, $^{232}U$ has a decay chain of short-lived
daughter products that undergo intense beta and gamma radiation.
The French nuclear program utilizes a fraction (1/3) of reprocessed uranium as fuel \cite{IAEA_management_2007}.
However for this simulation the reprocessed uranium is simply stockpiled.

>>>>

\begin{figure}[htbp!]
        \begin{center}
                \includegraphics[width=\columnwidth]{./images/french-transition/power_plot.png}
        \end{center}
        \caption{Timeseries of installed capacity of \gls{SFR}s}
        \label{fig:sfr_cap}
\end{figure}
\FloatBarrier

\begin{figure}[htbp!]
        \begin{center}
                \includegraphics[width=\columnwidth]{./images/french-transition/number_plot.png}
        \end{center}
        \caption{Timeseries of number of \gls{SFR}s}
        \label{fig:sfr_num}
\end{figure}
\FloatBarrier

@@
